\documentclass[10pt,a4paper]{article}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[default]{lato}
\usepackage[top=0.6in,bottom=0.6in,left=0.7in,right=0.7in]{geometry}
\usepackage{xcolor}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{microtype}
\definecolor{accent}{RGB}{190,30,45}
\setlength{\parindent}{0pt}
\pagestyle{empty}

\newcommand{\cvsection}[1]{%
  \vspace{8pt}%
  \noindent{\large\bfseries\color{accent}#1\hspace{6pt}}%
  {\color{black!25}\leavevmode\leaders\hrule height 0.5ex depth -0.4ex\hfill\kern0pt}%
  \par\vspace{3pt}%
}

\begin{document}

{\centering
  {\fontsize{38}{46}\fontseries{l}\selectfont Jing }%
  {\fontsize{38}{46}\bfseries Cheng}\par
  \vspace{4pt}
  {\small\color{accent}\scshape Software Engineer \textperiodcentered\ AI Tooling}\par
  \vspace{2pt}
  {\small\itshape Mannheim – Baden-Württemberg, Germany, 68159}\par
  \vspace{4pt}
  {\small
    +49 152 26552167   \enspace|\enspace
    \href{mailto:jingc.dev@gmail.com}{jingc.dev@gmail.com} \enspace|\enspace
    \href{https://github.com/KtfwyCJ}{github.com/KtfwyCJ} \enspace|\enspace
    \href{https://www.linkedin.com/in/jing-cheng-1a892310b/}{linkedin.com/in/jing-cheng-1a892310b/}\enspace|\enspace
    \href{https://jing-cj.cn/}{jing-cj.cn} 
  }\par
  \vspace{8pt}
}

\vspace{8pt}

\cvsection{Summary}

Software Engineer with 6+ years of experience building scalable web platforms, developer tooling, and AI-assisted engineering systems. Specialized in TypeScript-based frontend architecture, full-stack application development, and LLM-powered workflows including RAG and AI agents.

\vspace{6pt}

\cvsection{Work Experience}

\noindent\textbf{SAP SE (Hyperspace department)}\hfill\textit{Walldorf}\\
{ Software Engineer (work study)}\hfill{\small\itshape May. 2025 -- Present}
\begin{itemize}[leftmargin=*,topsep=2pt,itemsep=1pt,parsep=0pt]
  \item Engineered an autonomous AI-driven \textbf{Code Remediation Agent} in \textbf{Go} using the Eino framework, capable of analyzing GitHub Advanced Security findings, generating contextual fixes, and automatically creating remediation pull requests within developer workflows.

  \item Designed and implemented a retrieval-augmented generation (\textbf{RAG}) platform in \textbf{Python} for internal engineering knowledge access, integrating documentation ingestion pipelines, semantic retrieval, and \textbf{MCP server} interfaces to support AI-assisted development tooling.

  \item Researched and prototyped integration strategies between \textbf{Hyperspace tooling} and \textbf{Application Foundation} services, focusing on scalable \textbf{CI/CD} workflows, AI application lifecycle management, and internal platform extensibility.

  \item Extended a \textbf{CAP}-based internal prototyping platform with dynamic feature-toggle capabilities, enabling controlled experimentation.
\end{itemize}

\vspace{4pt}
\noindent\textbf{Nanjing WaterStone Information Technology Co.}\hfill\textit{Nanjing, China}\\
{\scshape\small Senior Software Engineer}\hfill{\small\itshape Apr. 2021 –- Sep. 2024}
\begin{itemize}[leftmargin=*,topsep=2pt,itemsep=1pt,parsep=0pt]
  \item Architected and delivered a real-time enterprise messaging platform based on Rocket.Chat, designing scalable WebSocket communication workflows and modern frontend systems with \textbf{Vue3} and \textbf{TypeScript} for responsive cross-platform collaboration experiences.

  \item Engineered reactive backend infrastructure using \textbf{Spring WebFlux}, optimizing high-concurrency \textbf{RESTful APIs}, \textbf{MySQL} read/write separation, and containerized \textbf{Docker} deployment pipelines for reliable production operations.

  \item Built and standardized internal developer tooling and frontend scaffolding frameworks with \textbf{Node.js}, \textbf{Babel}, and \textbf{esbuild}, accelerating project bootstrapping, improving engineering consistency, and reducing repetitive configuration effort across teams.

\end{itemize}

\vspace{4pt}
\noindent\textbf{AirBook Information Technology Co.}\hfill\textit{Nanjing, China}\\
{\scshape\small Software Engineer}\hfill{\small\itshape Sep.2020 –- Apr.2021}
\begin{itemize}[leftmargin=*,topsep=2pt,itemsep=1pt,parsep=0pt]
  \item Developed and maintained content management platforms using \textbf{React.js}, \textbf{Redux}, and Ant Design Pro, delivering modular and responsive frontend experiences for internal business operations.

  \item Designed and implemented reusable frontend component libraries, including Form, Video Player, and Loading modules, improving UI consistency and accelerating feature delivery across projects.

  \item Integrated \textbf{Google Analytics} and user behavior tracking workflows to support product analytics, usage monitoring, and data-driven operational decision-making.

\end{itemize}

\vspace{4pt}

\noindent\textbf{Nanjing Wishare Information Technology Co.}\hfill\textit{Nanjing, China}\\
{\scshape\small Junior Software Engineer}\hfill{\small\itshape Jul.2018 –- Sep.2020}
\begin{itemize}[leftmargin=*,topsep=2pt,itemsep=1pt,parsep=0pt]
  \item  Developed sports venue booking and ticketing platforms with \textbf{Vue.js} and \textbf{Webpack}, implementing core ticketing logic and reusable components.Built responsive web interfaces and optimized cross-device user experience.
  \item  Developed a venue booking mini-program with \textbf{mpvue}, supporting customizable themes and waterfall-style image displays.
\end{itemize}

\vspace{6pt}

\cvsection{Education}

\noindent\textbf{University of Mannheim}\hfill\textit{Mannheim}\\
{\scshape\small Master, Business Informatics}\hfill{\small\itshape Sep. 2024 -- 2026 (thesis remaining)}
\begin{itemize}[leftmargin=*,topsep=2pt,itemsep=1pt,parsep=0pt]
  \item Focus on Machine Learning, Large-scale Data, Large Language Models (LLMs), and Computer Vision

  \item \textbf{Master Thesis}: Revisiting Texture--Shape Bias: The Impact of Benchmark Construction Methods on Measured Visual Bias in Modern Vision Models

  \item \textbf{Selected Research Projects}:
  \begin{itemize}[leftmargin=1.2em,itemsep=0pt,topsep=1pt]
      \item From Implicit Procedure to Deliberate Planning: A Comparative Study of Different Stages of Multimodal Reasoning
      \item Historical Reliability of Large Language Models: A Red-Teaming Approach
  \end{itemize}
\end{itemize}

\noindent\textbf{Zhongbei College of Nanjing Normal University }\hfill\textit{Nanjing, China}\\
{\scshape\small Bachelor, Information Management and Information System}\hfill{\small\itshape Sep.2014 – Jun.2018}

\cvsection{Research Activity}
\vspace{4pt}
\begin{tabular*}{\linewidth}{@{}l@{\extracolsep{\fill}}r@{}}
\textbf{Historical LLM Workshop Presenter} & \textit{Sep 2025, ETH Zurich} \\
\end{tabular*}
\textbf{Topic: Constraining Historical Knowledge in Large Language Models: Comparing Prompting, Fine-Tuning and Pre-Training} \\
Presented research on mitigating historical hallucinations in LLMs through prompting, fine-tuning, and pre-training strategies.


\vspace{6pt}

\cvsection{Skills}

\begin{tabular}{@{}l@{\quad}l@{}}
\textbf{Languages}: TypeScript, JavaScript, Python, Java, SQL, Go(basic) \\
\textbf{Frontend}: React, Vue.js, Redux, Vite/Webpack \\
\textbf{Backend}: Node.js, Spring Boot, Spring WebFlux, REST APIs,MySQL, MongoDB \\
\textbf{DevOps Tools}: Docker, GitHub Actions, CI/CD, Git \\
\textbf{AI/LLM}: AI Agents, RAG Infrastructure, MCP, LLM Workflow Orchestration, 
Semantic Retrieval, LangChain, PyTorch
\end{tabular}

\vspace{6pt}

\cvsection{Languages}

\begin{tabular}{@{}l@{\quad}l@{}}
\textbf{English:} Full Professional Proficiency \\
\textbf{Chinese:} Native or Bilingual Proficiency \\
\textbf{German:} Elementary level \\
\end{tabular}

\vspace{6pt}

\cvsection{Interest}

\begin{tabular}{@{}l@{\quad}l@{}}
\textbf{Photography:} Landscape and Documentary \\
\textbf{Hiking:} Enjoy exploring scenic trails, and challenging terrains \\
\textbf{Jigsaw Puzzles:} Matsumoto Tadashi-style Jigsaw Puzzles \\
\end{tabular}



\end{document}